\textbf{Computational Fuzzy Extractors}

### 2013-05-20 CompFuzzExt.tex
Thm 5.4 revised...

\begin{theorem}
\label{thm:lossless secure extractor log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.    Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric over the alphabet of $Z$ size $2^b$, where the  block length $b = \log (2n^3 (c+2d)/d)=O(\log n)$.  Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c+2d)n/d}=O(n)$.  If GAPSVP and SIVP are hard to approximate within polynomial factors (on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds.
\consref{cons:informal construction} is a $(\M, bm, bm, t)$  fuzzy extractor that is $(\epsilon, s_{sec})$  hard with error $\delta = e^{-\Omega(n)}$.
Sketch takes $O(n^2)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3})$ operations over $\Fq$.
% for following parameters:
%\[
%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
%\] 
\end{theorem}
\begin{proof}
Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}. For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
\end{proof}

@@

>>>>

\begin{theorem}
\label{thm:lossless secure extractor log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.    Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric over the alphabet of $Z$ size $2^b$, where the  block length $b = \log (2n^3 (c+2d)/d)=O(\log n)$.  Let $W$ be uniform over $\mathcal{M}=Z^m$, where $m={(c+2d)n/d}=O(n)$.  If GAPSVP and SIVP are hard to approximate within polynomial factors (on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec}=\poly(n)$ there exists $\epsilon=\ngl(n)$ such that the following holds.
\consref{cons:informal construction} is a $(\M, bm, bm, t)$  fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$.
Sketch takes $O(n^2)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3})$ operations over $\Fq$.
% for following parameters:
%\[
%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
%\] 
\end{theorem}
\begin{proof}
Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}. For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
\end{proof}

@@

\begin{theorem}
\label{thm:lossless block sketch log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in\mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d)$.  Let $\alpha \leq n/3$, and let $W$ be $m$-symbol fixing source over $\zo^{\left((c+2d)n/d+\alpha \right)b})$.  If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/6$) using quantum algorithms, then  there is a setting of $q = \poly(n)$ such that for any polynomial $s_{sec} = \poly(n)$
 there exists $\epsilon = \ngl(n)$ such that the following holds: 
\consref{cons:informal construction} is a $(\M, mb, mb, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$-hard with error $\delta = e^{-\Omega(n)}$. Sketch takes $O(n^3\log n)$ operations over $\Fq$, and recover takes expected time $O(n^{4d+3} \log n)$ operations over $\Fq$.
\end{theorem}
